
\section{Implementation Blueprint}

\input{figures/fig_enforcement_stack}

A practical Continuity implementation has two layers. The first layer is human-readable Markdown or YAML front matter. The second layer is deterministic validation.

\subsection{Example file header}

\begin{lstlisting}
---
continuity_type: state
scope: repository
loads_on: boot
mutability: overwrite-current
updates_after:
  - architecture_change
  - task_completion
  - failed_assumption
validation:
  - max_lines: 180
  - no_unresolved_placeholders
  - no_conflicting_status
---
\end{lstlisting}

\subsection{Hooks and validators}

A useful implementation should provide at least five checks.
\begin{enumerate}
  \item \textbf{Pre-load budget checks} stop archive files or oversized manifests from loading by default.
  \item \textbf{Pre-action scope checks} verify that the agent has loaded the nearest relevant state chain.
  \item \textbf{Post-action reconciliation checks} flag when code changed but \statefile{STATE.md} or \statefile{TODO.md} did not.
  \item \textbf{Artifact checks} reject task completion without evidence links, test output, or commits.
  \item \textbf{Safety checks} detect nested files that weaken parent safety rules.
\end{enumerate}

\subsection{Promotion rules}

Generated state should not become canonical automatically. A run summary written by an agent can seed \file{LEARNINGS.md} or \file{completed/}, but promotion into \statefile{STATE.md} or repository-wide memory should pass through review, linting, and freshness checks.

\subsection{Why this layer matters}

The implementation layer prevents the central category error of the whole topic: confusing readable text with reliable control. Continuity is strongest when the repository shows the state and the surrounding tooling checks that the state still makes sense.
