
\section{Evaluation Agenda}

\input{figures/fig_evaluation_matrix}

The right evaluation target is not "does any context file help?" The right target is narrower: under what conditions does a compact, validated state layer improve repository work, and when does it become overhead?

\subsection{Conditions}

The core conditions are baseline (no repository state), manifest-only, minimal Continuity, minimal Continuity with hooks, full topology, and failure modes such as stale state, bloated context, and conflicting local instructions.

\subsection{Benchmarks and tasks}

Existing repository benchmarks such as \SWEbench{} remain useful for patch correctness \cite{Jimenez2024SWEbench}. They do not, however, measure resumption, repeated-error avoidance, or multi-agent collision. CONTINUITY therefore needs a custom task family with interruptions, stale-state traps, cross-branch handoffs, and malicious or noisy context.

\subsection{Metrics}

\input{tables/table_evaluation_metrics}

The most interesting metrics are often not the headline ones. Task success matters, but so do resumption latency, repeated-error rate, evidence completeness, human review time, and collision frequency.

\subsection{Ablations}

Ablations should remove \statefile{STATE.md}, \statefile{TODO.md}, \statefile{LEARNINGS.md}, scoped loading, evidence requirements, and validation hooks. Additional ablations should intentionally inject context bloat, stale facts, and local instruction conflicts.

\subsection{Expected shape of the results}

The expected positive result is modest: faster restarts, better handoff, cleaner audit trails, and fewer repeated failures. The expected negative result is equally important: larger context topologies should cost more and may perform worse. A credible paper should publish both.
